### 2014-12-07 Draft/abstract.tex
updated Intro
Updated RQ1

Temporal constraints of an Application Programming Interface (API)
are the allowed sequences of method invocations in the API.
These constraints govern the secure and robust operation of client software using the API.
However, in practice, most API do not have formal temporal constraints.
In contrast, these constraints are typically described
informally in natural language API documents and therefore are not amenable
to existing program analysis tools that require formal constraints.
\textit{The goal of this work is to assist developers construct API clients that comply with 
temporal constraints of the API through the inference and formalization of these constraints found in natural language text in API documents.}
Since, API documents are often verbose manually writing formal temporal constraints can be prohibitively time consuming and error prone.
To address this issue,
we propose \tool, a Machine Learning (ML) and Natural Language Processing (NLP) based
approach to identify and infer formal temporal constraints.
To evaluate our approach, we apply \tool\ to infer and formalize temporal
constraints from \amazonAPI, \paypalAPI\ and commonly used package \CodeIn{java.io} in the
JDK API.
Our results indicate that \tool\ is effective in identifying constraint sentences (from over
4000 human-annotated API sentences) with the average precision, recall, and F-score
of 65.0\%, 72.2\%, and 68.4\%, respectively.
Furthermore, \tool\ also achieves an accuracy of 70\% in inferring 63 formal temporal constraints from these sentences.

%Our approach also includes a novel
%technique of identifying method references (improvement over keyword-based
%techniques) in the natural language text by building domain
%dictionaries systematically from API documents and generic English
%dictionaries.
%
%
%Existing software engineering tools can leverage
%the inferred formal temporal constraints to effectively assist in development
%and verification activities.

%Temporal constraints of an Application Programming
%Interface (API) are the allowed sequences of invocations
%of methods from the API.
%These constraints govern the secure and robust
%operation of client software using the API.
%Typically, these constraints are described in natural language text
%of API documents and thus cannot be used by existing verification tools,
%which typically accept only formal constraints.
%Because manually writing temporal constraints based on
%API documents can be prohibitively time consuming and error prone,
%we propose \tool: a Natural Language Processing (NLP) based approach
%to automatically infer temporal constraints.
%In particular, our approach includes a novel technique to reduce the number of lexical tokens
%as a way to make API documents amenable to existing NLP techniques
%(which are typically designed to work on well-written news articles).
%Our approach also includes a novel technique of identifying method references in
%the natural language text by building domain dictionaries systematically
%from API documents and generic English dictionaries.
%To evaluate our approach, we apply \tool\ to infer temporal constraints from 
%commonly used package \CodeIn{java.io} in the JDK API and from the \amazonAPI.
%Our results show that \tool\ effectively identifies constraint sentences (from over 3900 API sentences) with the average precision, recall, and F-score of 65.0\%, 72.2\%, and 68.4\%, respectively.
%Furthermore, \tool\ also achieves an accuracy of 70\% in inferring 63 temporal constraints from these sentences.

% There are existing techniques that infer from API documents resource specifications 
% (such as constraints based on phases: creating, manipulating, and releasing resources).
% However, such techniques are limited to finding temporal specification of resources.
% Furthermore, such techniques do not make a distinction between explicit ordering of methods
% within each phases.

% where do you loose precision and recall.
\end{abstract}

>>>>

Temporal constraints of an Application Programming Interface (API)
are the allowed sequences of method invocations in the API.
These constraints govern the secure and robust operation of client software using the API.
However, in practice, most API do not have formal temporal constraints.
In contrast, these constraints are typically described
informally in natural language API documents and therefore are not amenable
to existing program analysis tools that require formal constraints.
\textit{The goal of this work is to assist developers construct API clients that comply with 
temporal constraints of the API through the inference and formalization of these constraints found in natural language text in API documents.}
Since, API documents are often verbose manually writing formal temporal constraints can be prohibitively time consuming and error prone.
To address this issue,
we propose \tool, a Machine Learning (ML) and Natural Language Processing (NLP) based
approach to identify and infer formal temporal constraints.
To evaluate our approach, we apply \tool\ to infer and formalize temporal
constraints from \amazonAPI, \paypalAPI\ and commonly used package \CodeIn{java.io} in the
JDK API.
Our results indicate that \tool\ is effective in identifying constraint sentences (from over
4000 human-annotated API sentences) with the average precision, recall, and F-score
of 77.0\%, 60.0\%, and 65.0\%, respectively.
Furthermore, \tool\ also achieves an accuracy of 70\% in inferring 63 formal temporal constraints from these sentences.

\end{abstract}

### 2014-12-07 Draft/approach.tex
Updated RQ1

The goal of model construction is to use a small set of manually classified temporal constraint sentences of a representative API to construct a model to automatically classify the unlabeled sentences. Since \tool\ seeks to achieve a binary classification of the API sentences, we chose to train our model using na{\"i}ve Bayes classifier which is the simplest probabilistic classification methods  and is shown to be comparative other advanced classification methods given appropriate prepossessing~\cite{rennie2003tackling}. The model can be trained offline or else by the users of the approach if better accuracy is required for specific data.

Feature selection is an important factor for the accuracy any classification method. Particularly, for na{\"i}ve Bayes classifier which assumes each feature independently contributes towards the final probability of classification. In the simplest form, each word occurring in a sentence is considered as a feature. However, such an approach may lead to overly specific models, and therefore \tool\ approach employs preprocessing for generic features. We next describe the features we chose for training our model along with the rationale for selecting such features.

>>>>

The goal of model construction is to use a small set of manually classified temporal constraint sentences of a representative API to construct a model to automatically classify the unlabeled sentences. 
We can any of the standard off-the-shelf classifiers to train the model, since \tool\ seeks to achieve only a binary classification of the API sentences.
For instance, model can be trained using na{\"i}ve Bayes classifier which is the simplest probabilistic classification methods  and is shown to be comparative other advanced classification methods given appropriate prepossessing~\cite{rennie2003tackling}. The model can be trained offline or else by the users of the approach if better accuracy is required for specific data.

Feature selection is an important factor for the accuracy any classification method. For instance, na{\"i}ve Bayes classifier assumes each feature independently contributes towards the final probability of classification. In the simplest form, each word occurring in a sentence is considered as a feature. However, such an approach may lead to overly specific models, and therefore \tool\ approach employs preprocessing for generic features. We next describe the features we chose for training our model along with the rationale for selecting such features.

### 2014-12-07 Draft/conclusion.tex
Updated RQ1

Despite being highly desirable, most APIs are not equipped with formal temporal constraints.
In contrast, documentation of API methods contains detailed specifications of temporal constraints in natural language text.
Manually writing formal specifications based on natural language text in API documents is prohibitively time consuming and error prone.
To address this issue, we have proposed a novel approach called \tool\ to infer temporal constraints from natural language text of API documents.
We applied \tool\ to infer temporal constraints from
\paypalAPI, \amazonAPI, and  
commonly used package \CodeIn{java.io} in the JDK API.
Our evaluation results show that \tool\ effectively identifies sentences describing
temporal constraints with an average 65\% precision and 72\% recall,
from more than 4000 sentences in subject API documents.
Furthermore, \tool\ also achieved an accuracy of
70\% in inferring 63 formal temporal constraints from these sentences.

>>>>

Despite being highly desirable, most APIs are not equipped with formal temporal constraints.
In contrast, documentation of API methods contains detailed specifications of temporal constraints in natural language text.
Manually writing formal specifications based on natural language text in API documents is prohibitively time consuming and error prone.
To address this issue, we have proposed a novel approach called \tool\ to infer temporal constraints from natural language text of API documents.
We applied \tool\ to infer temporal constraints from
\paypalAPI, \amazonAPI, and  
commonly used package \CodeIn{java.io} in the JDK API.
Our evaluation results show that \tool\ effectively identifies sentences describing
temporal constraints with an average 77\% precision and 60\% recall,
from more than 4000 sentences in subject API documents.
Furthermore, \tool\ also achieved an accuracy of
70\% in inferring 63 formal temporal constraints from these sentences.

### 2014-12-07 Draft/evaluation.tex
Updated RQ1

\subsection{Evaluation Setup} 
We first manually annotated the sentences in the API documents of the two APIs.
Two authors manually labeled each sentence in the API documentation as sentence containing 
temporal constraints or not.
We used \CodeIn{cohen kappa}~\cite{carletta1996assessing} score to statistically measure
the inter-rater agreement.
The \CodeIn{cohen kappa} score of the two authors was .66 (on a scale of 0 to 1), 
which denotes a statically significant agreement~\cite{carletta1996assessing}. 
After the authors classified all the sentences, they 
discussed with each other to reach a consensus on the sentences they classified differently. 
We use these classified sentences as the golden set for calculating precision and recall.

To answer RQ1, we measure the number of true positives ($TP$), false positives ($FP$), true negative ($TN$), and false negatives ($FN$)
in identifying the constraint sentences by \tool.
We define constraint sentence as a sentence describing a temporal constraints.
We define the $TP$, $FP$, $TN$, and $FN$ of \tool\ as follows:

@@

In statistical classification~\cite{Olson08}, \CodeIn{precision} is defined as a ratio of
number of true positives to the total number of items reported to be true,
\CodeIn{recall} is defined as a ratio of number of true positives to the total number
of items that are true. \CodeIn{F-Score} is defined as the weighted harmonic mean of 
\CodeIn{precision} and \CodeIn{recall}. Higher value of \CodeIn{precision}, \CodeIn{recall}, and \CodeIn{F-Score}
are indicative of higher quality of the constraint statements inferred using 
\tool. based on the calculation of $TP$, $FP$, $TN$, and $FN$ of \tool\ defined
previously we computed the \CodeIn{precision}, \CodeIn{recall}, and \CodeIn{F-Score} of \tool\ as follows:

@@

@@

\begin{tabular}{rlccccccccc}
\topline
\headcol S. No. & Trainer	& P$_{wrd}$	& R$_{wrd}$	& F$_{wrd}$	& P$_{ftr}$	& R$_{ftr}$	& F$_{ftr}$	& P$_{\Delta}$	& R$_{\Delta}$	& F$_{\Delta}$	\\
\midline 
		 1 		& 				& 662 	& 2417 		& 78 		& 88 		& 57 		& 31 		& 21 			& 64.8 			& 73.1 			\\ 
\rowcol  2		& \amazonAPI 	& 662 	& 2417 		& 78 		& 88 		& 57 		& 31 		& 21 			& 64.8 			& 73.1 			\\ 
		 3		& \paypalAPI 	& 662 	& 2417 		& 78 		& 88 		& 57 		& 31 		& 21 			& 64.8 			& 73.1 			\\ 
\rowcol 		& Average 		& 662 	& 2417 		& 78 		& 88 		& 57 		& 31 		& 21 			& 64.8 			& 73.1 			\\ 
\bottomlinec
%----------------- END TABLE DATA ------------------------ 
\multicolumn{11}{p{6.5in}}{\small
All values are average over 10-fold cross validation;
P: Precision; R: Recall; F: F-Score;
$_{wrd}$: No features used for training;
$_{ftr}$: features used for training;
$_{\Delta}$: improvement factor ($_{ftr}$ - $_{wrd}$)} \\ 
\end{tabular}
\label{tab:results}
\end{center}
\end{table*}

@@

In this section, we quantify the effectiveness of \tool\ in identifying constraint sentences by answering RQ1.
Table~\ref{tab:results} shows the effectiveness of \tool\ in identifying constraint sentences.
Column ``API'' lists the names of the subject API. 
Columns ``Mtds'' and ``Sen'' lists the number of methods and sentences in each subject API's.
Column ``Sen$_C$'' list the number of manually identified constraint sentences.
Column ``Sen$_{ICON}$'' lists the number of sentences identified by \tool\ as constraint sentences. 
Columns ``TP'', ``FP'', ``TN'', and ``FN'' represent the number of \CodeIn{true positives}, \CodeIn{false positives}, \CodeIn{true negatives}, and \CodeIn{false negatives}, respectively. 
Columns ``P(\%)'', ``R(\%)'', and ``F$_S$(\%)'' list percentage values of \CodeIn{precision}, \CodeIn{recall}, and \CodeIn{F-score} respectively. 
Our results show that, out of 3,909 sentences, \tool\ effectively identifies constraint sentences with the average \CodeIn{precision}, \CodeIn{recall}, and \CodeIn{F-score} of 65.0\%, 72.2\%, and 68.4\%, respectively.

%We next present an example to illustrate how \tool\ incorrectly identifies a sentence as a constraint sentence. \textbf{A example goes here}
We next present an example to illustrate how \tool\ incorrectly identifies a sentence as a constraint sentence (producing false positives).
For instance, consider the sentence ``\textit{This is done by flushing the stream and then closing the underlying output stream.}'' from  \CodeIn{close} method description from \CodeIn{PrintStream} class.
\tool\ incorrectly identifies the action ``flush'' being performed before the action ``close''.
However \tool\ fails to make the distinction that it happens internally (enforced in the body) in the method.
\tool, thus incorrectly identifies the sentence as a constraint sentence.

Another major source of FPs is the incorrect parsing of sentences by the underlying NLP infrastructure
and/or inadequacy of generic dictionaries for synonym analysis.
For instance, consider the sentence ``\textit{If this stream has an associated channel then the channel is closed as well.}''
from the \CodeIn{close} method description from \CodeIn{FileOutputStream}.
The sentence describes an effect that happens as a result of calling the \CodeIn{close} method and does not describe any temporal constraint.
However, \tool\ annotates the sentence as a constraint sentence because underlying Wordnet dictionaries matches the word ``has'' as a synonym of ``get''.
This incorrect matching in turn causes \tool\ to incorrectly annotate the sentence as constraint sentence
because ``has'' is matched against \CodeIn(get) method in \CodeIn{FileOutputStream}.
We observed 8 instances of previously described example in our results.

If we manually fixed the Wordnet dictionaries to not match ``has'' and ``get'' as synonyms,
our precision is further increased to 70.8\% effectively increasing the F-Score of \tool\ to 71.2\%.
Although an easy fix, we refrained from including such modifications for reporting the results to stay true to our approach.
In the future, we plan to investigate techniques to construct better domain dictionaries for software API.

We next present an example to illustrate how \tool\ fails identify a constraint sentence (producing false negative).
False negatives are undesirable in the context of our problem domain
because they can mislead the users of \tool\ into believing that no other temporal constraint exists in the API documents.
Furthermore, an overwhelming number of false negatives works against the practicality of \tool.
For instance, consider the sentence ``\textit{This implementation of the PUT operation creates a copy of an object that is already stored in Amazon S3.}''
from  \CodeIn{PUT Object-Copy} method description in \amazonAPI.
The sentence describes the constraint that the object must already be stored (invocation of \CodeIn{PUT Object})
before calling the current method.
However, \tool cannot make the connection owing to the limitation of the semantic graphs that do not list ``already stored'' as a ``valid operation'' on object.  
In the future, we plan to investigate techniques to further improve knowledge graphs to infer such implicit constraints.

Another major source of false negatives (similar to reasons for false positives) is the incorrect parsing of sentences by the underlying NLP infrastructure.
For instance, consider the sentence ``\textit{If any in-memory buffering is being done by the application (for example, by a BufferedOutputStream object),
those buffers must be flushed into the FileDescriptor (for example, by invoking OutputStream.flush) before that data will be affected by sync.}''
The sentence describes that the \CodeIn{OutputStream.flush()} must be invoked before invoking the current method if in-memory buffering is performed.
However, the length and complexity in terms of number of clauses causes the underlying Stanford parser to inaccurately annotate the dependencies,
which eventually results into incorrect classification.

Overall, a significant number of false positives and false negatives will be reduced as the current NLP research advances the underlying NLP infrastructure.
Furthermore, use of domain specific dictionaries as opposed to generic dictionaries
sed in current prototype implementation will further improve the precision and recall of \tool.

@@

In this section, we evaluate the effectiveness of \tool\ in inferring temporal constraints from the identified constraint sentences from API documents.Table~\ref{tab:results} shows the effectiveness of \tool\ in inferring temporal constraints from the identified constraint sentences.
Column ``API'' lists the names of the subject API. 
Columns ``Mtds'' and ``Sen'' list the number of methods and sentences in each subject API's.
Column ``Sen$_C$'' lists the number of manually identified constraint sentences.
Column ``Spec$_{ICON}$'' lists the number of sentences with correctly inferred temporal constraints by \tool. 
Column ``Acc(\%)'' list percentage values of accuracy. 
Our results show that, out of 90 manually identified constraint sentences, \tool\ correctly infers temporal constraints with the average accuracy of 70.0\%.

>>>>

\subsection{Evaluation Setup} 
We first manually annotated the sentences in the API documents of the subject APIs.
First two authors manually labeled each sentence in the Java API documentation as sentence containing 
temporal constraints or not.
We used \CodeIn{cohen kappa}~\cite{carletta1996assessing} score to statistically measure
the inter-rater agreement.
The \CodeIn{cohen kappa} score of the two authors was .66 (on a scale of 0 to 1), 
which denotes a statically significant agreement~\cite{carletta1996assessing}. 
Based on the discussions first author annotated the rest of the subject APIs. 
After the authors classified all the sentences, they 
discussed with each other to reach a consensus on the sentences they classified differently. 
We use these classified sentences as the golden set for evaluating effectiveness of \tool.
Table~\ref{tab:results} lists the subject statistics.

To answer RQ1, we first measure the number of true positives ($TP$), false positives ($FP$), true negative ($TN$), and false negatives ($FN$)
in identifying the constraint sentences by \tool.
We define constraint sentence as a sentence describing a temporal constraints.
We define the $TP$, $FP$, $TN$, and $FN$ of \tool\ as follows:

@@

In statistical classification~\cite{Olson08}, \CodeIn{precision} is defined as a ratio of
number of true positives to the total number of items reported to be true,
\CodeIn{recall} is defined as a ratio of number of true positives to the total number
of items that are true. \CodeIn{F-Score} is defined as the weighted harmonic mean of 
\CodeIn{precision} and \CodeIn{recall}.
Based on the calculation of $TP$, $FP$, $TN$, and $FN$ of \tool\ defined
previously we computed the \CodeIn{precision}, \CodeIn{recall}, and \CodeIn{F-Score} of \tool\ as follows:

@@

We then use these measures to identify relative effectiveness of \tool by executing multiple classifiers on the annotated sentences.
We tested the classifiers using a stratified n-fold cross-validation approach,
using 10 as the value n (10-fold) as recommended by Han et al.~\cite{han2006data}
The cross validation ensures that every sentence is used for training and testing,
thus producing low bias and variance.
In particular, we execute the classifiers in two different configurations.
First we execute the classifiers using the words in the sentnces as features and measure \CodeIn{precision}, \CodeIn{recall}, and \CodeIn{F-Score} as P$_{wrd}$, R$_{wrd}$, and F$_{wrd}$.
We next execute the classifiers on the features proposed by \tool\ approach and measure \CodeIn{precision}, \CodeIn{recall}, and \CodeIn{F-Score} as P$_{ftr}$, R$_{ftr}$, and F$_{ftr}$.
We next calculate relative gain in \CodeIn{precision}, \CodeIn{recall}, and \CodeIn{F-Score} as P$_{\Delta}$ (P$_{ftr}$- P$_{wrd}$), R$_{\Delta}$ (R$_{ftr}$ - R$_{wrd}$), and F$_{\Delta}$ (F$_{ftr}$ - F$_{wrd}$). 
Higher values of P$_{\Delta}$, R$_{\Delta}$, and F$_{\Delta}$ are are indicative of effectiveness of the constraint statements inferred using \tool.

@@

\begin{tabular}{rlccccccccc}
\topline
\headcol S. No. & Trainer	& P$_{wrd}$	& R$_{wrd}$	& F$_{wrd}$	& P$_{ftr}$	& R$_{ftr}$	& F$_{ftr}$	& P$_{\Delta}$	& R$_{\Delta}$	& F$_{\Delta}$	\\
\midline 
1	& AdaBoost	& 0.52	& 0.81	& 0.61	& 0.7	& 0.78	& 0.74	& 0.18	& -0.03	& 0.13	\\
\rowcol2	& NaiveBayes	& 0.49	& 0.67	& 0.56	& 0.74	& 0.65	& 0.69	& 0.25	& -0.02	& 0.13	\\
3	& Balanced Winnow	& 0.77	& 0.76	& 0.76	& 0.78	& 0.77	& 0.77	& 0.01	& 0.01	& 0.01	\\
\rowcol4	& Decision Tree	& 0.82	& 0.58	& 0.66	& 0.92	& 0.41	& 0.56	& 0.1	& -0.17	& -0.1	\\
5	& Winnow	& 0.19	& 0.41	& 0.15	& 0.8	& 0.51	& 0.59	& 0.61	& 0.1	& 0.44	\\
\rowcol6	& MaxEnt	& 0.69	& 0.48	& 0.55	& 0.76	& 0.46	& 0.56	& 0.07	& -0.02	& 0.01	\\
	& Total	& 0.59	& 0.62	& 0.55	& 0.77	& 0.6	& 0.65	& 0.19	& -0.02	& 0.1	\\
\bottomlinec
%----------------- END TABLE DATA ------------------------ 
\multicolumn{11}{p{5in}}{\small
All values are average over 10-fold cross validation;
P: Precision; R: Recall; F: F-Score;
$_{wrd}$: No features used for training;
$_{ftr}$: features used for training;
$_{\Delta}$: improvement factor ($_{ftr}$ - $_{wrd}$)} \\ 
\end{tabular}
\label{tab:resultsRQ1}
\end{center}
\end{table*}

@@

In this section, we quantify the effectiveness of \tool\ in identifying constraint sentences by answering RQ1.
Table~\ref{tab:results} shows the effectiveness of \tool\ in inferring temporal constraints from the identified constraint sentences using various classifiers.
Column ``Trainer'' lists the names of the classifiers used to train the model for classifications in \tool.
Columns P$_{wrd}$, R$_{wrd}$, and F$_{wrd}$ list the \CodeIn{precision}, \CodeIn{recall}, and \CodeIn{F-score} of classifiers trained without the features proposed by \tool.
Columns P$_{ftr}$, R$_{ftr}$, and F$_{ftr}$ list the \CodeIn{precision}, \CodeIn{recall}, and \CodeIn{F-score} of classifiers trained with the features proposed by \tool.
Finally, columns P$_{\Delta}$, R$_{\Delta}$, and F$_{\Delta}$ list the improvement factors in\CodeIn{precision}, \CodeIn{recall}, and \CodeIn{F-score} respectively.

For our evaluation we used following well known classifiers: AdaBoost (or adaptive boosting), Na{\"i}ve Bayes, Winnow, Balanced Winnow, Decision Tree, and Max Entropy. We used Na{\"i}ve Bayes as the weaker classifier with AdaBoost. We used \CodeIn{Mallet}~\cite{mallet} implementation of these classifiers for our experiments.

Our results show that, \tool\ effectively identifies constraint sentences with the average (across different classifiers) \CodeIn{precision}, \CodeIn{recall}, and \CodeIn{F-score} of 77.0\%, 60.0\%, and 65.0\%, respectively.
Balanced Winnow performed best, with an average \CodeIn{precisoin} and \CodeIn{recall} of 78\% and 77\% respectively. 
Furthermore, our results also show the features proposed by \tool\ improves the precision of classification algorithms by an average of 19\%, without significant reduction in the recall (average 2\%).

%We next present an example to illustrate how \tool\ incorrectly identifies a sentence as a constraint sentence. \textbf{A example goes here}
%We next present an example to illustrate how \tool\ incorrectly identifies a sentence as a constraint sentence (producing false positives).
%For instance, consider the sentence ``\textit{This is done by flushing the stream and then closing the underlying output stream.}'' from  \CodeIn{close} method description from \CodeIn{PrintStream} class.
%\tool\ incorrectly identifies the action ``flush'' being performed before the action ``close''.
%However \tool\ fails to make the distinction that it happens internally (enforced in the body) in the method.
%\tool, thus incorrectly identifies the sentence as a constraint sentence.   
%
%
%Another major source of FPs is the incorrect parsing of sentences by the underlying NLP infrastructure
%and/or inadequacy of generic dictionaries for synonym analysis.
%For instance, consider the sentence ``\textit{If this stream has an associated channel then the channel is closed as well.}''
%from the \CodeIn{close} method description from \CodeIn{FileOutputStream}.
%The sentence describes an effect that happens as a result of calling the \CodeIn{close} method and does not describe any temporal constraint.
%However, \tool\ annotates the sentence as a constraint sentence because underlying Wordnet dictionaries matches the word ``has'' as a synonym of ``get''.
%This incorrect matching in turn causes \tool\ to incorrectly annotate the sentence as constraint sentence
%because ``has'' is matched against \CodeIn(get) method in \CodeIn{FileOutputStream}.
%We observed 8 instances of previously described example in our results.
%
%If we manually fixed the Wordnet dictionaries to not match ``has'' and ``get'' as synonyms,
%our precision is further increased to 70.8\% effectively increasing the F-Score of \tool\ to 71.2\%.
%Although an easy fix, we refrained from including such modifications for reporting the results to stay true to our approach.
%In the future, we plan to investigate techniques to construct better domain dictionaries for software API. 
%
%We next present an example to illustrate how \tool\ fails identify a constraint sentence (producing false negative).
%False negatives are undesirable in the context of our problem domain
%because they can mislead the users of \tool\ into believing that no other temporal constraint exists in the API documents.
%Furthermore, an overwhelming number of false negatives works against the practicality of \tool.
%For instance, consider the sentence ``\textit{This implementation of the PUT operation creates a copy of an object that is already stored in Amazon S3.}''
%from  \CodeIn{PUT Object-Copy} method description in \amazonAPI.
%The sentence describes the constraint that the object must already be stored (invocation of \CodeIn{PUT Object})
%before calling the current method.
%However, \tool cannot make the connection owing to the limitation of the semantic graphs that do not list ``already stored'' as a ``valid operation'' on object.  
%In the future, we plan to investigate techniques to further improve knowledge graphs to infer such implicit constraints. 
%
%Another major source of false negatives (similar to reasons for false positives) is the incorrect parsing of sentences by the underlying NLP infrastructure.
%For instance, consider the sentence ``\textit{If any in-memory buffering is being done by the application (for example, by a BufferedOutputStream object),
%those buffers must be flushed into the FileDescriptor (for example, by invoking OutputStream.flush) before that data will be affected by sync.}''
%The sentence describes that the \CodeIn{OutputStream.flush()} must be invoked before invoking the current method if in-memory buffering is performed.
%However, the length and complexity in terms of number of clauses causes the underlying Stanford parser to inaccurately annotate the dependencies,
%which eventually results into incorrect classification. 
%
%Overall, a significant number of false positives and false negatives will be reduced as the current NLP research advances the underlying NLP infrastructure.
%Furthermore, use of domain specific dictionaries as opposed to generic dictionaries
%used in current prototype implementation will further improve the precision and recall of \tool.

@@

In this section, we evaluate the effectiveness of \tool\ in inferring temporal constraints from the identified constraint sentences from API documents.Table~\ref{tab:results} shows the effectiveness of \tool\ in inferring temporal constraints from the identified constraint sentences.
Column ``Trainer'' lists the names of the subject API. 
Columns ``Mtds'' and ``Sen'' list the number of methods and sentences in each subject API's.
Column ``Sen$_C$'' lists the number of manually identified constraint sentences.
Column ``Spec$_{ICON}$'' lists the number of sentences with correctly inferred temporal constraints by \tool. 
Column ``Acc(\%)'' list percentage values of accuracy. 
Our results show that, out of 90 manually identified constraint sentences, \tool\ correctly infers temporal constraints with the average accuracy of 70.0\%.
